---
title: "Code for credit fraud detection with data mining"
subtitle: |
  | By Hua-Wei Huang, 2020
  | outputs are not displayed, please refer to the report

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```


```{r}
# Import library and dataset

library(dplyr)
library(VIM)
library(tidyverse)
library(ggplot2)
library(mice)
library(fBasics)
library(Metrics)
library(MASS)
library(ISLR)
library(leaps)
library(glmnet)
library(klaR)

setwd("your own working directory")
ori_train_data <- read.table("cs-training.csv", header = TRUE,
                             sep = ",",row.names = 1)
```

```{r}

# Rename columns 

colnames(ori_train_data)[which(names(ori_train_data) == "SeriousDlqin2yrs")] <- "default"
colnames(ori_train_data)[which(names(ori_train_data) == "MonthlyIncome")] <- "monthly_income"
colnames(ori_train_data)[which(names(ori_train_data) == "NumberOfDependents")] <- "num_dependents"
colnames(ori_train_data)[which(names(ori_train_data) == "RevolvingUtilizationOfUnsecuredLines")] <- "unsecured_lines"
colnames(ori_train_data)[which(names(ori_train_data) == "NumberOfTime30.59DaysPastDueNotWorse")] <- "past_due_30"
colnames(ori_train_data)[which(names(ori_train_data) == "NumberOfTime60.89DaysPastDueNotWorse")] <- "past_due_60"
colnames(ori_train_data)[which(names(ori_train_data) == "DebtRatio")] <- "debt_ratio"
colnames(ori_train_data)[which(names(ori_train_data) == "NumberOfOpenCreditLinesAndLoans")] <- "credit_lines"
colnames(ori_train_data)[which(names(ori_train_data) == "NumberOfTimes90DaysLate")] <- "late_90"
colnames(ori_train_data)[which(names(ori_train_data) == "NumberRealEstateLoansOrLines")] <- "real_estate"

```


# Exploratory data analysis

reference: https://cran.r-project.org/web/packages/dlookr/vignettes/EDA.html
```{r}

# basic statistic summary
round(basicStats(ori_train_data),3)

# visualising missing patterns
library(naniar)

cols_missing <- ori_train_data[,c("monthly_income", "num_dependents")]
vis_miss(cols_missing)

# visualising correlation
cor_ori_train <- cor(ori_train_data[,1:11])

library(corrplot)
corrplot(cor_ori_train, method="circle")

# visualising normality
library(dlookr)
plot_normality(ori_train_data)
```
# Histogram

```{r}
par(mfrow = c(2,2))
hist(ori_train_data$unsecured_lines, n = 30, xlab = "unsecured_lines", 
     main = "Histogram of unsecured_lines")
hist(ori_train_data$age, n = 30, xlab = "age", 
     main = "Histogram of age")
hist(ori_train_data$past_due_30, n = 30, xlab = "past_due_30",
     main = "Histogram of past_due_30")
hist(ori_train_data$debt_ratio, n = 50, xlab = "debt_ratio",
     main = "Histogram of debt_ratio")

hist(ori_train_data$monthly_income, xlab = "monthly_income",
     main = "Histogram of monthly_income")
hist(ori_train_data$credit_lines, n = 50, xlab = "credit_lines",
     main = "Histogram of credit_lines")
hist(ori_train_data$late_90, n = 50, xlab = "late_90",
     main = "Histogram of late_90")
hist(ori_train_data$real_estate, n = 50, xlab = "real_estate",
     main = "Histogram of real_estate")


par(mfrow = c(2,1))
hist(ori_train_data$past_due_60, n = 50, xlab = "past_due_60",
     main = "Histogram of past_due_60")
hist(ori_train_data$num_dependents, n = 50, xlab = "num_dependents",
     main = "Histogram of num_dependents")
```

### Boxplots
```{r, fig.width=22, fig.height=12}

no_missing_income <- ori_train_data[!is.na(ori_train_data$monthly_income),]
no_missing_dependent <- ori_train_data[!is.na(ori_train_data$num_dependents),]

par(mfrow=c(2,2))

#unsecured_lines

unsecured_lines.y.bp <- c(ori_train_data$unsecured_lines, 
                          no_missing_dependent$unsecured_lines, 
                          no_missing_income$unsecured_lines)

unsecured_lines.x.np <- c(rep(1,length(ori_train_data$unsecured_lines)),
                          rep(2,length(no_missing_dependent$unsecured_lines)),
                          rep(3,length(no_missing_income$unsecured_lines)))


boxplot(unsecured_lines.y.bp ~ unsecured_lines.x.np, 
        col=c("white","skyblue2","green2"),
        names=c(" \n All data \n n = 150000","Remove missing dependents \n n = 146076","Remove missing monthly income \n n = 120269"), 
        pch = 19, boxwex = 0.5, 
        ylab = "unsecured_lines", 
        main = "unsecured_lines boxplots with different datasets")




#AGE

age.y.bp <- c(ori_train_data$age, 
              no_missing_dependent$age, 
              no_missing_income$age)

age.x.np <- c(rep(1,length(ori_train_data$age)),
              rep(2,length(no_missing_dependent$age)),
              rep(3,length(no_missing_income$age)))

boxplot(age.y.bp ~ age.x.np, col=c("white","skyblue2","green2"),
        names=c(" \n All data \n n = 150000","Remove missing dependents \n n = 146076","Remove missing monthly income \n n = 120269"), 
        pch = 19, boxwex = 0.5, 
        ylab = "Age", 
        main = "Age boxplots with different datasets")



#past_due_30

past_due_30.y.bp <- c(ori_train_data$past_due_30, 
                      no_missing_dependent$past_due_30, 
                      no_missing_income$past_due_30)

past_due_30.x.np <- c(rep(1,length(ori_train_data$past_due_30)),
                      rep(2,length(no_missing_dependent$past_due_30)),
                      rep(3,length(no_missing_income$past_due_30)))

boxplot(past_due_30.y.bp ~ past_due_30.x.np, 
        col=c("white","skyblue2","green2"),
        names=c(" \n All data \n n = 150000","Remove missing dependents \n n = 146076","Remove missing monthly income \n n = 120269"), 
        pch = 19, boxwex = 0.5, 
        ylab = "past_due_30", 
        main = "past_due_30 boxplots with different datasets")



#debt_ratio

debt_ratio.y.bp <- c(ori_train_data$debt_ratio, 
                     no_missing_dependent$debt_ratio, 
                     no_missing_income$debt_ratio)

debt_ratio.x.np <- c(rep(1,length(ori_train_data$debt_ratio)),
                     rep(2,length(no_missing_dependent$debt_ratio)),
                     rep(3,length(no_missing_income$debt_ratio)))

boxplot(debt_ratio.y.bp ~ debt_ratio.x.np, 
        col=c("white","skyblue2","green2"),
        names=c(" \n All data \n n = 150000","Remove missing dependents \n n = 146076","Remove missing monthly income \n n = 120269"), 
        pch = 19, boxwex = 0.5,
        ylab = "debt_ratio", 
        main = "debt_ratio boxplots with different datasets")



#credit_lines

credit_lines.y.bp <- c(ori_train_data$credit_lines,
                       no_missing_dependent$credit_lines, 
                       no_missing_income$credit_lines)

credit_lines.x.np <- c(rep(1,length(ori_train_data$credit_lines)),
                       rep(2,length(no_missing_dependent$credit_lines)),
                       rep(3,length(no_missing_income$credit_lines)))

boxplot(credit_lines.y.bp ~ credit_lines.x.np, 
        col=c("white","skyblue2","green2"),
        names=c(" \n All data \n n = 150000","Remove missing dependents \n n = 146076","Remove missing monthly income \n n = 120269"), 
        pch = 19, boxwex = 0.5,
        ylab = "credit_lines", 
        main = "credit_lines boxplots with different datasets")



#late_90

late_90.y.bp <- c(ori_train_data$late_90, 
                  no_missing_dependent$late_90, 
                  no_missing_income$late_90)

late_90.x.np <- c(rep(1,length(ori_train_data$late_90)),
                  rep(2,length(no_missing_dependent$late_90)),
                  rep(3,length(no_missing_income$late_90)))

boxplot(late_90.y.bp ~ late_90.x.np, 
        col=c("white","skyblue2","green2"),
        names=c(" \n All data \n n = 150000","Remove missing dependents \n n = 146076","Remove missing monthly income \n n = 120269"), 
        pch = 19, boxwex = 0.5,
        ylab = "late_90", 
        main = "late_90 boxplots with different datasets")



#real_estate

real_estate.y.bp <- c(ori_train_data$real_estate, 
                      no_missing_dependent$real_estate, 
                      no_missing_income$real_estate)

real_estate.x.np <- c(rep(1,length(ori_train_data$real_estate)),
                      rep(2,length(no_missing_dependent$real_estate)),
                      rep(3,length(no_missing_income$real_estate)))

boxplot(real_estate.y.bp ~ real_estate.x.np, 
        col=c("white","skyblue2","green2"),
        names=c(" \n All data \n n = 150000","Remove missing dependents \n n = 146076","Remove missing monthly income \n n = 120269"), 
        pch = 19, boxwex = 0.5,
        ylab = "real_estate", 
        main = "real_estate boxplots with different datasets")



#past_due_60

past_due_60.y.bp <- c(ori_train_data$past_due_60, 
                      no_missing_dependent$past_due_60, 
                      no_missing_income$past_due_60)

past_due_60.x.np <- c(rep(1,length(ori_train_data$past_due_60)),
                      rep(2,length(no_missing_dependent$past_due_60)),
                      rep(3,length(no_missing_income$past_due_60)))

boxplot(past_due_60.y.bp ~ past_due_60.x.np, 
        col=c("white","skyblue2","green2"),
        names=c(" \n All data \n n = 150000","Remove missing dependents \n n = 146076","Remove missing monthly income \n n = 120269"), 
        pch = 19, boxwex = 0.5, 
        ylab = "past_due_60", 
        main = "past_due_60 boxplots with different datasets")
```

# Exploring outliers and missing values in each variable

## unsecured_lines
```{r}
exploration_data <- ori_train_data

#cut unsecured lines into groups
labs <- c(paste(seq(0, 28, by = 2), seq(0 + 2 - 1, 30 - 1, by = 2),
                sep = "-"), paste(30, "+", sep = ""))

exploration_data$unsecured_lines_group <- cut(exploration_data$unsecured_line, breaks = c(seq(0, 30, by = 2), Inf), labels = labs, right = FALSE)

unsecured_table<- exploration_data %>%
  group_by(unsecured_lines_group) %>%
  summarise(n=n())

# evaluate the table and the trend in unsecured_lines
unsecured_table

# evaluate proportion of default 
unsecured_default <- exploration_data %>%
  dplyr::filter(unsecured_lines >=15) %>%
  summarise(proportion = mean(default), n = n())

unsecured_default2 <- exploration_data %>%
  dplyr::filter(unsecured_lines <15) %>%
  summarise(proportion = mean(default), n = n())

```

## real_estate
```{r}
# explore real_estate values
estate_table <- exploration_data %>%
  group_by(real_estate) %>%
  summarise(n = n())

estate_table
```

## credit_lines
```{r}
#cut credit_lines into groups
labs <- c(paste(seq(0, 45, by = 5), seq(0 + 45 - 1, 50 - 1, by = 5),
                sep = "-"), paste(50, "+", sep = ""))

exploration_data$credit_lines_group <- cut(exploration_data$credit_lines, breaks = c(seq(0, 50, by = 5), Inf), labels = labs, right = FALSE)

#evaluate credit_lines
credit_table <- exploration_data %>%
  group_by(credit_lines_group) %>%
  summarise(n=n())

credit_table
```

## debt_ratio
```{r}

#evaluate proportion of default with dataset containing different percentile 
debt_table1 <- exploration_data %>%
  summarise(proportion = mean(default), n = n())

debt_boundary_97 <-  quantile(ori_train_data$debt_ratio, probs = 0.975)
debt_boundary_95 <-  quantile(ori_train_data$debt_ratio, probs = 0.95)

debt_table2 <- exploration_data %>%
  dplyr::filter(debt_ratio<= debt_boundary_97) %>%
  summarise(proportion = mean(default), n = n())

debt_table3 <- exploration_data %>%
  dplyr::filter(debt_ratio<= debt_boundary_95) %>%
  summarise(proportion = mean(default), n = n())

#combind result in a table
debt_table <- rbind(debt_table1, debt_table2, debt_table3)
debt_table
```

## late payment
```{r}
#explore late payment variables
late_payment_table <- exploration_data %>%
  dplyr::filter(past_due_30 >= 90 & past_due_60 >= 90 & late_90 >=90)
```


# Truncation

```{r}
#truncate late payment
clean_train_data <- ori_train_data %>%
  dplyr::filter(past_due_30 < 96 | past_due_60 < 96 | late_90 < 96)

# credit_lines range
Q1.credit <- quantile(clean_train_data$credit_lines, probs = 0.25)
Q2.credit <- quantile(clean_train_data$credit_lines, probs = 0.5)
Q3.credit <- quantile(clean_train_data$credit_lines, probs = 0.75)

upper.cut.credit <- Q2.credit + 3*((Q3.credit - Q1.credit)/(2*0.6745))
lower.cut.credit <- Q2.credit - 3*((Q3.credit - Q1.credit)/(2*0.6745))


# real_estate range
Q1.estate <- quantile(clean_train_data$real_estate, probs = 0.25)
Q2.estate <- quantile(clean_train_data$real_estate, probs = 0.5)
Q3.estate <- quantile(clean_train_data$real_estate, probs = 0.75)

upper.cut.estate <- Q2.estate + 3*((Q3.estate - Q1.estate)/(2*0.6745))
lower.cut.estate <- Q2.estate - 3*((Q3.estate - Q1.estate)/(2*0.6745))

# age range
Q1.age <- quantile(clean_train_data$age, probs = 0.25)
Q2.age <- quantile(clean_train_data$age, probs = 0.5)
Q3.age <- quantile(clean_train_data$age, probs = 0.75)

upper.cut.age <- Q2.age + 3*((Q3.age - Q1.age)/(2*0.6745))
lower.cut.age <- Q2.age - 3*((Q3.age - Q1.age)/(2*0.6745))

# debt_ratio range
upper.cut.debt <-  quantile(clean_train_data$debt_ratio, probs = 0.975)

# monthly_income range
upper.cut.income <-quantile(clean_train_data$monthly_income, probs = 0.975, na.rm = T)

# num_dependents range
upper.cut.dependents <-quantile(clean_train_data$num_dependents, probs = 0.975, na.rm = T)

# truncate variables

clean_train_data2 <- clean_train_data %>%
  dplyr::filter(credit_lines >= lower.cut.credit & credit_lines <= upper.cut.credit) %>%
  dplyr::filter(real_estate >= lower.cut.estate & real_estate <= upper.cut.estate) %>%
  dplyr::filter(debt_ratio <= upper.cut.debt) %>%
  dplyr::filter(monthly_income <= upper.cut.income | is.na(monthly_income)) %>%
  dplyr::filter(num_dependents <= upper.cut.dependents | is.na(num_dependents)) %>%
  dplyr::filter(age >= lower.cut.age & age <= upper.cut.age)

# replace unsecured_lines outliers with NA
clean_train_data2$unsecured_lines[clean_train_data2$unsecured_lines >= 15] <- NA

```



# Imputation

This part is imputation for the missing values in monthly_income, num_dependents, and unsecured_lines
```{r}

# make 1 datasets with 5 iterations using predictive mean matching

temp_train_data <- mice(clean_train_data2,m=1,maxit=5,meth='pmm',seed=500)

# complete the dataset

train_complete_data = complete(temp_train_data, action=1)
```

# Visualising final clean data
```{r}
# visualising correlation
cor_complete_data <- cor(train_complete_data[,1:11])

library(corrplot)
corrplot(cor_complete_data, method="circle")


#histogram
par(mfrow = c(2,2))
hist(train_complete_data$unsecured_lines, n = 30, xlab = "unsecured_lines", 
     main = "Histogram of unsecured_lines")
hist(train_complete_data$age, n = 30, xlab = "age", 
     main = "Histogram of age")
hist(train_complete_data$past_due_30, n = 30, xlab = "past_due_30",
     main = "Histogram of past_due_30")
hist(train_complete_data$debt_ratio, n = 50, xlab = "debt_ratio",
     main = "Histogram of debt_ratio")

hist(train_complete_data$monthly_income, xlab = "monthly_income",
     main = "Histogram of monthly_income")
hist(train_complete_data$credit_lines, n = 50, xlab = "credit_lines",
     main = "Histogram of credit_lines")
hist(train_complete_data$late_90, n = 50, xlab = "late_90",
     main = "Histogram of late_90")
hist(train_complete_data$real_estate, n = 50, xlab = "real_estate",
     main = "Histogram of real_estate")

par(mfrow = c(2,1))
hist(train_complete_data$past_due_60, n = 50, xlab = "past_due_60",
     main = "Histogram of past_due_60")
hist(train_complete_data$num_dependents, n = 50, xlab = "num_dependents",
     main = "Histogram of num_dependents")

# basic statistics
round(basicStats(train_complete_data),3)
```

# Information value
https://www.r-bloggers.com/woe-and-iv-variable-screening-with-information-in-r/
```{r}
infoTables <- create_infotables(data = train_complete_data,

                               y = "default",
                              bins = 10,
                              parallel = T)

# – Plot IV

plotFrame <- infoTables$Summary[order(-infoTables$Summary$IV), ]
plotFrame$Variable <- factor(plotFrame$Variable,

                            levels = plotFrame$Variable[order(-plotFrame$IV)])

ggplot(plotFrame, aes(x = Variable, y = IV)) +
geom_bar(width = .35, stat = "identity") +
ggtitle("Information value of each variable") +
theme_bw() +
theme(plot.title = element_text(size = 10)) +
theme(axis.text.x = element_text(angle = 90))

plotFrame$Variable
plotFrame$IV
```

# Splitting into training and test data
```{r}

# creates a value for dividing the data into train and test. 
# The training value is defined as 75% of the dataset

sample.size = floor(0.75*nrow(train_complete_data))  

set.seed(1003)   # set seed to ensure having same random numbers generated


# Randomly identifies the rows equal to sample size from  all the rows of AutoPart dataset and stores the row number in train_ind

train_ind = sample(seq_len(nrow(train_complete_data)),size = sample.size)  

final_train_data = train_complete_data[train_ind,] #creates the training dataset with row numbers in train_ind
final_test_data = train_complete_data[-train_ind,]  # creates the test dataset excluding the row numbers in train_ind
```

# Model fit

## Logistic Regression
https://cran.r-project.org/web/packages/dominanceanalysis/vignettes/da-logistic-regression.html
```{r}

library(dominanceanalysis)

glm_fit <- glm(default~., data=final_train_data, family=binomial(link='logit'))

# predict
glm_prob <- predict(glm_fit, final_test_data, type="response")
glm_pred <- ifelse(glm_prob > 0.5, 1, 0)

glm_CM <- table(glm_pred, final_test_data$default)
glm_accuracy <- 1- mean(glm_pred != final_test_data$default)

glm_rmse <- rmse(as.numeric(final_test_data$default), as.numeric(glm_pred))

```

## LDA
```{r}

LDA_fit <- lda(default~., data = final_train_data)

# prediction and confusion table

LDA_pred <- predict(LDA_fit, final_test_data)

LDA_CM <- table(LDA_pred$class, final_test_data$default)
LDA_accuracy <- 1- mean(LDA_pred$class != final_test_data$default)  # error rate


LDA_rmse <- rmse(final_test_data$default, as.numeric(LDA_pred$class))
```

## QDA
```{r}
QDA_fit <- qda(default~., data = final_train_data)


# prediction and confusion table

QDA_pred <- predict(QDA_fit, final_test_data)

QDA_CM <- table(QDA_pred$class, final_test_data$default)
QDA_accuracy <- 1 - mean(QDA_pred$class != final_test_data$default)  # error rate

QDA_rmse <- rmse(final_test_data$default, as.numeric(QDA_pred$class))
```

## LASSO
```{r}

library(glmnet)
library(caret)

x.train <- model.matrix(default~., final_train_data)[,-1]
y.train <- final_train_data$default

x.test <- model.matrix(default~., final_test_data)[,-1]
y.test <- final_test_data$default

cv.lasso <- cv.glmnet(x.train, y.train, alpha = 1, type.measure = "mae")
plot(cv.lasso)

lasso.best.lam =cv.lasso$lambda.min
lasso.best.lam

lasso.model <- glmnet(x.train, y.train, alpha = 1, family = "binomial")
lasso.coef <- coef(lasso.model,s=lasso.best.lam)[,1]


lasso.prob <- predict(lasso.model, newx = x.test, s = lasso.best.lam)
lasso.pred <- ifelse(lasso.prob > 0.5, 1, 0)

(lasso_info2 <- postResample(lasso.pred, y.test))



lasso_CM <- table(lasso.pred, final_test_data$default)
lasso_accuracy <- mean(lasso.pred == final_test_data$default)

lasso_rmse <- rmse(final_test_data$default, lasso.pred)
```

## Random forest 
https://www.blopig.com/blog/2017/04/a-very-basic-introduction-to-random-forests-using-r/
https://www.listendata.com/2014/11/random-forest-with-r.html#Preparing-Data-for-Random-Forest

```{r}

#import the package
library(randomForest)

final_train_data$default <- as.factor(final_train_data$default)
final_test_data$default <- as.factor(final_test_data$default)

# Perform training:
rf_fit = randomForest(default ~ ., data = final_train_data, 
                             ntree=100, mtry=2, importance=TRUE)

# Validation set assessment #1: looking at confusion matrix

rf_pred <- predict(rf_fit, final_test_data, type = "class")


# Checking classification accuracy
rf_accuracy <- mean(rf_pred == final_test_data$default)                    
rf_CM <- table(rf_pred,final_test_data$default)


rf_rmse <- rmse(as.numeric(final_test_data$default), as.numeric(rf_pred))
```

##Decision tree

https://stats.stackexchange.com/questions/105760/how-we-can-draw-an-roc-curve-for-decision-trees

https://medium.com/analytics-vidhya/a-guide-to-machine-learning-in-r-for-beginners-decision-trees-c24dfd490abb#:~:text=A%20Decision%20Tree%20is%20a,(Classification%20%26%20Regression%20Trees).

https://www.datacamp.com/community/tutorials/decision-trees-R

```{r}

library(tree)

tree_fit <- tree(default~., data = final_train_data)
tree_pred <- predict(tree_fit, final_test_data, type = "class")


tree_CM <- table(tree_pred, final_test_data$default)
tree_accuracy <- mean(tree_pred == final_test_data$default) 

tree_rmse <-rmse(as.numeric(final_test_data$default), as.numeric(tree_pred))
```


## Neural Network

https://machinelearningmastery.com/non-linear-classification-in-r/
```{r}
library(nnet)

final_train_data$default <- as.factor(final_train_data$default)
final_test_data$default <- as.factor(final_test_data$default)


# fit model
NN_fit <- nnet(default~., data=final_train_data, size=10, decay=0.0001, maxit=500)

# summarize the fit
summary(NN_fit)

# make predictions
NN_pred <- predict(NN_fit, final_test_data, type="class")

# summarize accuracy
NN_CM <- table(NN_pred, final_test_data$default)

NN_accuracy <- mean(NN_pred == final_test_data$default) 

NN_rmse <-rmse(as.numeric(final_test_data$default), as.numeric(NN_pred))

```



## XGBoost
https://cran.r-project.org/web/packages/xgboost/vignettes/xgboostPresentation.html#measure-learning-progress-with-xgb.train

```{r}

library(xgboost)
library(ROCR)

gbm_train <- final_train_data

xgb_train_data <- xgb.DMatrix(data = as.matrix(final_train_data[,-1])
                      ,label = as.numeric(final_train_data$default)-1)

xgb_test_data <- xgb.DMatrix(data = as.matrix(final_test_data[,-1])
                    , label = as.numeric(final_test_data$default)-1)ef

watchlist <- list(train=xgb_train_data, test=xgb_test_data)

xgb_fit <- xgb.train(data=xgb_train_data, max.depth=3
                 , eta=0.01, nthread = 2, nround=2000
                 , watchlist=watchlist, eval.metric = "error"
                 , eval.metric = "logloss"
                 , objective = "binary:logistic")

print(xgb.importance(model = xgb_fit))

#plot importance
xgb.plot.importance(importance_matrix = xgb.importance(model = xgb_fit), 
                    xlab = "Relative importance (percentage)",
                    main = "Importance")

#model prediction
xgb_prob <- predict(xgb_fit,xgb_test_data)
xgb_pred <- ifelse(xgb_prob > 0.5, 1, 0)

# summarize accuracy
xgb_CM <- table(xgb_pred, final_test_data$default)

xgb_accuracy <- mean(xgb_pred == final_test_data$default)


#rmse

XGB_rmse <-rmse(as.numeric(final_test_data$default), as.numeric(xgb_pred))

```

# Creating table of accuracy
```{r}
accuracy_table <- data.frame(
  glm_accuracy = glm_accuracy,
  LDA_accuracy = LDA_accuracy,
  QDA_accuracy = QDA_accuracy,
  lasso_accuracy = lasso_accuracy,
  rf_accuracy = rf_accuracy,
  tree_accuracy = tree_accuracy,
  NN_accuracy = NN_accuracy,
  xgb_accuracy = xgb_accuracy
)


```

# Creating table of RMSE
```{r}
RMSE_table <- data.frame(
  glm_rmse = glm_rmse,
  LDA_rmse = LDA_rmse,
  QDA_rmse = QDA_rmse,
  lasso_rmse = lasso_rmse,
  rf_rmse = rf_rmse,
  tree_rmse = tree_rmse,
  NN_rmse = NN_rmse,
  XGB_rmse = XGB_rmse
)

RMSE_table
```

# All the confusion matrix
```{r}
glm_CM
LDA_CM
QDA_CM
lasso_CM

rf_CM
tree_CM
NN_CM
xgb_CM
```

# Calculating AUC
```{r}
# Logistic regression AUC
glm_auc <- prediction(glm_prob, final_test_data$default) %>%
  performance(measure = "auc") %>%
  .@y.values

# LDA AUC
LDA_auc <- prediction(LDA_pred$posterior[,2], final_test_data$default) %>% 
  performance(measure = "auc") %>%
  .@y.values

# QDA AUC
QDA_auc <- prediction(QDA_pred$posterior[,2], final_test_data$default) %>%
  performance(measure = "auc") %>%
  .@y.values

# Lasso auc
lasso_auc <- prediction(lasso.pred, final_test_data$default) %>%
  performance(measure = "auc") %>%
  .@y.values

# Random forest AUC
rf_auc <- prediction(as.numeric(rf_pred), final_test_data$default) %>%
  performance(measure = "auc") %>%
  .@y.values

# Decision tree AUC
tree_auc <- prediction(as.numeric(tree_pred), final_test_data$default) %>%
  performance(measure = "auc") %>%
  .@y.values

# Neural network AUC
NN_auc <- prediction(as.numeric(NN_pred), final_test_data$default) %>%
  performance(measure = "auc") %>%
  .@y.values

# xbg auc
xgb_auc <- prediction(xgb_pred, final_test_data$default) %>%
  performance(measure = "auc") %>%
  .@y.values
```

# Creating table of AUC
```{r}
AUC_table <- data.frame(
  glm_auc = glm_auc[[1]],
  LDA_auc = LDA_auc[[1]],
  QDA_auc = QDA_auc[[1]], 
  lasso_auc = lasso_auc[[1]], 
  rf_auc = rf_auc[[1]], 
  tree_auc = tree_auc[[1]], 
  NN_auc = NN_auc[[1]], 
  xgb_auc = xgb_auc[[1]]
)

AUC_table
```


# Importance plot for glm and VIF
```{r}

dapres<-dominanceAnalysis(glm_fit)

# plot for importance
plot(dapres, which.graph ="general",fit.function = "r2.m")
anova(glm_fit, test="Chisq")

#robustness
plot(glm_fit)

car::vif(glm_fit)
```

# Final model result

```{r}
round(summary(glm_fit)$coefficients,3)
round(anova(glm_fit, test="Chisq"),3)
```

